\documentclass[letterpaper,9pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to ensure 1-page fit
\addtolength{\oddsidemargin}{-0.60in}
\addtolength{\evensidemargin}{-0.60in}
\addtolength{\textwidth}{1.20in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.30in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{2pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Ayush Sanger} \\ \vspace{2pt}
    \small Noida, Uttar Pradesh, India $|$
    \href{mailto:sangerforbusiness@gmail.com}{\underline{sangerforbusiness@gmail.com}} $|$
    +91-8505875016 $|$
    \href{https://linkedin.com/in/ayushsanger}{\underline{linkedin.com/in/ayushsanger}} $|$
    \href{https://github.com/SangerForCode}{\underline{github.com/SangerForCode}}
\end{center}

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{BITS Pilani, Goa Campus}{Goa, India}
{B.E. (Hons.) Mathematics and Computing \& M.Sc. Chemistry \hfill \textbf{CGPA: 8.04}}{Aug. 2023 -- Aug. 2028}

\resumeSubheading
{Cambridge School}{Noida, India}
{CBSE (Class XII): \textbf{93.0\%} \;|\; CBSE (Class X): \textbf{95.2\%}}{2020 -- 2022}



\resumeSubHeadingListEnd
\resumeSubHeadingListEnd
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, TypeScript, SQL} \\
     \textbf{Core CS}{: Data Structures \& Algorithms, OOP, DBMS, System Design Fundamentals,Linear Algebra,Numerical Optimization} \\
     \textbf{Backend}{: Django, FastAPI, Flask, REST APIs, PostgreSQL, Authentication, RBAC, Background Jobs, API Integrations} \\
     \textbf{Frontend}{: React, Next.js, React Native, Expo, Tailwind CSS, HTML, CSS} \\
    \textbf{Cloud \& DevOps}{: AWS, Cloudflare, Docker, Linux, Git, GitHub Actions, CI/CD} \\
     \textbf{Data/ML}{: NumPy, Pandas, Scikit-learn, TensorFlow, Matplotlib, Time-Series Analysis} \\
     \textbf{Tools}{: Postman, Firebase, Supabase, MATLAB, Shoonya API}
    }}
\end{itemize}
\section{Leadership \& Awards}
\resumeSubHeadingListStart
    \resumeSubheading
      {Founder \& Chief Coordinator --- BITS Goa Sports Club (BGSC)}{Jun. 2025 -- Apr. 2026}
      {BITS Pilani, Goa Campus}{}
      \resumeItemListStart
        \resumeItem{Founded and led the campus sports ecosystem comprising \textbf{9 clubs} and \textbf{200+ committee members}.}
        \resumeItem{Executed \textbf{80+ events} while securing \textbf{INR 4 Lakh} in sponsorships and engaging \textbf{2,900+ participants}.}
        \resumeItem{Generated \textbf{300K+} social media impressions through digital campaigns.}
      \resumeItemListEnd

    
\resumeSubHeadingListEnd

\section{Experience}

\resumeSubHeadingListStart



\resumeSubheading
{Software Development Intern}{May 2026 -- Jul. 2026}
{Finoux}{Remote}
\resumeItemListStart
    \resumeItem{Improved API response time by \textbf{24\%} by optimizing \textbf{PostgreSQL} queries and simplifying database operations for backend services.}
    \resumeItem{Improved backend performance by \textbf{15\%} by refactoring existing code and resolving performance bottlenecks while maintaining \textbf{99.9\%} system availability.}
\resumeItemListEnd






\resumeSubheading
{Web Development Intern}{May 2025 -- Jul. 2025}
{Samvardhan Greenfields}{Remote}
\resumeItemListStart
\resumeItem{Built and deployed a lead management system on \textbf{AWS EC2} using \textbf{Amazon RDS (MySQL)} to automate customer enquiry handling and meeting scheduling.}
\resumeItem{Designed relational database schemas and implemented role-based workflows for sales operations, increasing qualified monthly customer contacts and scheduled sales calls by \textbf{78 \%}.}


\resumeItemListEnd





\resumeSubHeadingListEnd


\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{SWD Store BITS Pilani} $|$ \emph{Django, PostgreSQL, AWS, React}}{\href{https://swdstore.bits-pilani.ac.in}{{swdstore.bits-pilani.ac.in}}}
      \resumeItemListStart
        \resumeItem{Co-founded an officially adopted inter-campus marketplace serving \textbf{8,600+ users} across \textbf{4 BITS campuses} and processing \textbf{300,000 requests} every 12 days.}
        \resumeItem{Built \textbf{Google OAuth}, session authentication, institutional email verification, and role-based access controls for verified student transactions.}
        \resumeItem{Designed transaction-safe checkout and order-state workflows using \textbf{PostgreSQL} constraints and transactions to prevent inconsistent marketplace events.}
        \resumeItem{Implemented asynchronous notification workers for listing, checkout, and status-update events; deployed and maintained the platform on {AWS}.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{SyncQ Events} $|$ \emph{Next.js, PostgreSQL, Cloudflare}}{\href{https://syncqtech.com}{{syncqtech.com}}}
      \resumeItemListStart
        \resumeItem{Building a scalable event-management platform for registrations, schedules, \textbf{QR check-ins}, networking, announcements, and organizer workflows.}
        \resumeItem{Designed \textbf{PostgreSQL} schemas and API workflows for events, users, roles, check-ins, volunteer availability, and announcements.}
        \resumeItem{Implemented \textbf{RBAC}-backed organizer workflows and \textbf{Cloudflare}-backed deployment for reliable event operations.}
        \resumeItem{Developing an availability engine to reduce scheduling conflicts across clubs, volunteers, venues, and event time slots.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Algorithmic Trading Bot \& Backtesting Engine} $|$ \emph{Python, Shoonya API}}{June. 2025--July 2025}
      \resumeItemListStart
        \resumeItem{Built an event-driven options trading engine with modular strategy, broker, execution, and risk-management layers.}
        \resumeItem{Backtested strategies on \textbf{5 years} of historical data using trend, volume, stop-loss, and position-sizing rules.}
        \resumeItem{Implemented automated order execution with configurable risk limits, trade logging, and failure handling.}
      \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Behavioral Fitness Analytics Platform} $|$ \emph{Python, Streamlit, PostgreSQL, Linear Regression}}{March. 2025-May. 2026}
  \resumeItemListStart
    \resumeItem{Engineered a high-performance analytics platform using \textbf{Python} and \textbf{Streamlit} to process and visualize real-time fitness data across multiple workout modalities.}
    \resumeItem{Implemented a predictive weight-tracking engine using \textbf{Linear Regression} to forecast goal attainment dates by \textbf{statistical trend analysis}.}
    \resumeItem{Designed a normalized \textbf{PostgreSQL} database schema for multi-dimensional fitness telemetry and integrated A/B testing logic to evaluate feature performance and user engagement.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
\section{Awards}
\resumeSubHeadingListStart
    \resumeSubheading
      {Mantra Award Winner --- Social Leadership 2025--26}{July. 2026}
      {BITS Pilani}{}
      \resumeItemListStart
        \resumeItem{Sole recipient of the 2025--26 Social Leadership Mantra Award, recognizing campus-wide impact through BGSC; one of only \textbf{204 recipients} since 2009.}
      \resumeItemListEnd


\end{document}
```[cite: 7]